Learning to Infer Graphics Programs from Hand-Drawn Images

### 2017-07-21 paper.tex
improved example programs figure

\newcommand{\exampleProgramSize}{4.5cm} 
\newcommand{\exampleDrawingSize}{2cm}

\begin{figure}
  \begin{tabular}{m{4cm}ll}
    \toprule
    Drawing&Trace&Program\\
    \midrule
    \includegraphics[width = \exampleDrawingSize]{figures/expert-29-trim.png}&
\begin{minipage}{\exampleProgramSize}\begin{verbatim}
Line(2,15, 4,15)
Line(4,9, 4,13)
Line(3,11, 3,14)
Line(2,13, 2,15)
Line(3,14, 6,14)
Line(4,13, 8,13)
\end{verbatim}
\end{minipage}&     \begin{minipage}{\exampleProgramSize} \begin{verbatim}
for(i<3)
 line(i,-1*i+6, 2*i+2,-1*i+6)
 line(i,-2*i+4,i,-1*i+6)
       \end{verbatim}
     \end{minipage}&\\\midrule
     \includegraphics[width = \exampleDrawingSize]{figures/expert-52-trim.png}&
\begin{minipage}{\exampleProgramSize}\begin{verbatim}
Line(5,13, 2,10),
  arrow = True)
Circle(center = (5,9)
Circle(center = (8,5)
Line(2,8, 2,6), 
  arrow = True)
Circle(center = (2,5)
Circle(center = (5,14)
Circle(center = (2,9)
Line(5,13, 8,10), 
  arrow = True)
\end{verbatim}
\emph{... etc. ...}\\
\end{minipage}&
             \begin{minipage}{\exampleProgramSize}\begin{verbatim}
circle(4,10)
for(i<3)
 circle(-3*i+7,5)
 circle(-3*i+7,1)
 line(-3*i+7,4,-3*i+7,2,arrow=True)
 line(4,9,-3*i+7,6,arrow=True)
\end{verbatim}
\end{minipage}\\\midrule
    \includegraphics[width = \exampleDrawingSize]{figures/expert-38-trim.png}&
\begin{minipage}{\exampleProgramSize}\begin{verbatim}
Circle(center = (5,8)
Circle(center = (2,8)
Circle(center = (8,11)
Line(2,9, 2,10)
Circle(center = (8,8)
Line(3,8, 4,8)
Line(3,11, 4,11)
Line(8,9, 8,10)
Circle(center = (5,14)
Line(5,9, 5,10)
Circle(center = (2,14)
\end{verbatim}
  \emph{... etc. ...}\\
\end{minipage}&\begin{minipage}[t]{\exampleProgramSize}
\begin{verbatim}
for(i<3)
 for(j<3)
  if(j>0)
   line(-3*j+8,-3*i+7,-3*j+9,-3*i+7)
  line(-3*i+7,-3*j+8,-3*i+7,-3*j+9)
  circle(-3*j+7,-3*i+7)
\end{verbatim}
\end{minipage}\\\midrule
\includegraphics[width = \exampleDrawingSize]{figures/expert-75-trim.png}&
\begin{minipage}{\exampleProgramSize}\begin{verbatim}
Line(11,14, 13,14), 
  arrow = True)
Circle(center = (10,10)
Line(10,13, 10,11), 
  arrow = True)
Line(7,14, 9,14), 
  arrow = True)
Circle(center = (6,10)
Circle(center = (2,10)
Line(3,14, 5,14), 
  arrow = True)
\end{verbatim}
    \emph{... etc. ...}\\
\end{minipage}&
\begin{minipage}[t]{\exampleProgramSize}
    \begin{verbatim}
for(i<4)
 line(-4*i+13,4,-4*i+13,2,arrow=True)
 for(j<3)
  if(j>0)
   circle(-4*i+13,4*j+-3)
  line(-4*j+10,5,-4*j+12,5,arrow=True)
\end{verbatim}
  \end{minipage}\\\midrule

@@

\begin{minipage}{\exampleProgramSize}\begin{verbatim}
Circle(center = (2,8)
Rectangle(6,9, 7,10)
Circle(center = (8,8)
Rectangle(6,12, 7,13)
Rectangle(3,9, 4,10)
Circle(center = (2,14)
Circle(center = (8,14)
Circle(center = (5,11)
Rectangle(3,12, 4,13)
\end{verbatim}
  \end{minipage}&\begin{minipage}[t]{\exampleProgramSize}
\begin{verbatim}
reflect(y=8)
 for(i<3)
  if(i>0)
   rectangle(3*i-1,2,3*i,3)
  circle(3*i+1,3*i+1)
\end{verbatim}
\end{minipage}\\\bottomrule
  \end{tabular}
  \caption{Example drawings (left), their ground truth traces (middle), and programs synthesized from these traces (right). Note the nested loops in the Ising model, special case conditionals for the HMM, combination of symmetry and iteration in the bottom figure, and affine transformation in the top figure.}\label{exampleSynthesisResults}
  \end{figure}

>>>>

\newcommand{\exampleProgramSize}{6cm}
\newcommand{\exampleTraceSize}{4.5cm}
\newcommand{\exampleDrawingSize}{2cm}

\begin{figure}
  \begin{tabular}{m{2.5cm}ll}
    \toprule
    Drawing&Trace&Program\\
    \midrule
    \includegraphics[width = \exampleDrawingSize]{figures/expert-29-trim.png}&
\begin{minipage}{\exampleTraceSize}\begin{verbatim}
Line(2,15, 4,15)
Line(4,9, 4,13)
Line(3,11, 3,14)
Line(2,13, 2,15)
Line(3,14, 6,14)
Line(4,13, 8,13)
\end{verbatim}
\end{minipage}&     \begin{minipage}{\exampleProgramSize} \begin{verbatim}
for(i<3)
 line(i,-1*i+6, 2*i+2,-1*i+6)
 line(i,-2*i+4,i,-1*i+6)
       \end{verbatim}
     \end{minipage}&\\\midrule
     \includegraphics[width = \exampleDrawingSize]{figures/expert-52-trim.png}&
\begin{minipage}{\exampleTraceSize}\begin{verbatim}
Line(5,13, 2,10),
  arrow = True)
Circle(center = (5,9)
Circle(center = (8,5)
Line(2,8, 2,6), 
  arrow = True)
Circle(center = (2,5)
Circle(center = (5,14)
Circle(center = (2,9)
\end{verbatim}
\emph{... etc. ...}\\
\end{minipage}&
             \begin{minipage}{\exampleProgramSize}\begin{verbatim}
circle(4,10)
for(i<3)
 circle(-3*i+7,5)
 circle(-3*i+7,1)
 line(-3*i+7,4,-3*i+7,2,
      arrow=True)
 line(4,9,-3*i+7,6,
      arrow=True)
\end{verbatim}
\end{minipage}\\\midrule
    \includegraphics[width = \exampleDrawingSize]{figures/expert-38-trim.png}&
\begin{minipage}{\exampleTraceSize}\begin{verbatim}
Circle(center = (5,8)
Circle(center = (2,8)
Circle(center = (8,11)
Line(2,9, 2,10)
Circle(center = (8,8)
Line(3,8, 4,8)
Line(3,11, 4,11)
Line(8,9, 8,10)
Circle(center = (5,14)
\end{verbatim}
  \emph{... etc. ...}\\
\end{minipage}&\begin{minipage}{\exampleProgramSize}
\begin{verbatim}
for(i<3)
 for(j<3)
  if(j>0)
   line(-3*j+8,-3*i+7,-3*j+9,-3*i+7)
  line(-3*i+7,-3*j+8,-3*i+7,-3*j+9)
  circle(-3*j+7,-3*i+7)
\end{verbatim}
\end{minipage}\\\midrule
\includegraphics[width = \exampleDrawingSize]{figures/expert-75-trim.png}&
\begin{minipage}{\exampleTraceSize}\begin{verbatim}
Line(11,14, 13,14), 
  arrow = True)
Circle(center = (10,10)
Line(10,13, 10,11), 
  arrow = True)
Line(7,14, 9,14), 
  arrow = True)
Circle(center = (6,10)
Circle(center = (2,10)
\end{verbatim}
    \emph{... etc. ...}\\
\end{minipage}&
\begin{minipage}{\exampleProgramSize}
    \begin{verbatim}
for(i<4)
 line(-4*i+13,4,-4*i+13,2,
      arrow=True)
 for(j<3)
  if(j>0)
   circle(-4*i+13,4*j+-3)
  line(-4*j+10,5,-4*j+12,5,
       arrow=True)
\end{verbatim}
  \end{minipage}\\\midrule

@@

\begin{minipage}{\exampleTraceSize}\begin{verbatim}
Circle(center = (2,8)
Rectangle(6,9, 7,10)
Circle(center = (8,8)
Rectangle(6,12, 7,13)
Rectangle(3,9, 4,10)
Circle(center = (2,14)
Circle(center = (8,14)
Circle(center = (5,11)
Rectangle(3,12, 4,13)
\end{verbatim}
  \end{minipage}&\begin{minipage}{\exampleProgramSize}
\begin{verbatim}
reflect(y=8)
 for(i<3)
  if(i>0)
   rectangle(3*i-1,2,3*i,3)
  circle(3*i+1,3*i+1)
\end{verbatim}
\end{minipage}\\\bottomrule
  \end{tabular}
  \caption{Example drawings (left), their ground truth traces (middle), and programs synthesized from these traces (right). Compared to the trace the programs are more compressive and automatically group together related drawing commands. are Note the nested loops in the Ising model, special case conditionals for the HMM, combination of symmetry and iteration in the bottom figure, and affine transformation in the top figure.}\label{exampleSynthesisResults}
  \end{figure}
